%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {FutureVault} % Organization
    {Toronto, ON} % Location
    {Sept. 2023 - Dec. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Proposed and implemented a system for the creation and provisioning of sets of bookmarks tailored for specific user groups using React.js, Spring Boot, and MongoDB, optimizing user workflows and information access.}
        \item {Spearheaded the design and deployment of a favicon scraper, enhancing the visual representation of the in-app bookmarks tab.}
        \item {Created a drag and drop form UI in React.js for bookmark template creation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Radar} % Organization
    {New York, NY} % Location
    {Jan. 2023 - Apr. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led mobile SDK work in Android, iOS, and React Native for tracking conversions, clearly demonstrating return on investment for customers while providing important leverage for renegotiating partnerships.}
        \item {Spearheaded project to add hours of operation to geofences, designing intuitive frontend components and introducing robust modifications to critical business logic.}
        \item {Created developer productivity tools for an internal React Native testing app to coordinate complex builds involving several codebases, reducing iteration time by 80\%.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Android Mobile Developer} % Job title
    {theScore} % Organization
    {Toronto, ON} % Location
    {Jan. 2022 - Apr. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Redesigned app widget to address user feedback and maintain functionality across different device types.}
        \item {Constructed queries for GraphQL as part of a transition away from REST, adding support for live updates with subscriptions.}
        \item {Worked with product team to implement and coordinate UI changes across Android and iOS platforms.}
        \item {Maintained low technical debt by writing thorough unit tests.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Android Infotainment Projection Software Developer} % Job title
    {Ford Motor Company} % Organization
    {Waterloo, ON} % Location
    {May 2021 - Aug. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed Apple CarPlay application for Android Automotive OS in-vehicle infotainment system.}
        \item {Implemented media playback for iPhone over wireless CarPlay, as well as exposing media control API using standard Android MediaBrowserService interface.}
        \item {Designed responsive landing page for Apple CarPlay app.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Android Software Developer} % Job title
    {BlackBerry} % Organization
    {Waterloo, ON} % Location
    {Jan. 2020 - Apr. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented MS Exchange functionality in Blackberry Hub Inbox, Services, Calendar, Contacts, Notes, and Tasks apps, each with more than 1 million downloads on Google Play.}
        \item {Added security checks for user account creation, improving resilience against brute force password cracking.}
        \item {Diagnosed and resolved bugs for improved user experience and security.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
